\section{Grading}

Final grades for this project is obtained in the following way:


\begin{itemize}
  \item Performance: 20\%.
  \item Energy use: 20\%.
  \item Unit tests: 10\%.
  \item Functional tests: 5\%.
  \item Design quality: 5\%.
  \item Code quality: 10\%.
  \item Performance and energy evaluation in the report: 15\%.
  \item Work organization: 10\%.
  \item Conclusions: 5\%.  
\end{itemize}

\textgood{RELEVANT WARNINGS}:

\begin{itemize}
  \item If the submitted code does not compile, 
        the final grade for the project will be 0.

  \item If a quality coding rule is ignored without justification,
        the final grade for the project will be 0.
        
  \item In case of copying all implied groups will get a grade of 0.
        Beside the head of the school will be notified for
        the corresponding disciplinary actions.
\end{itemize}

\section{Submission procedures}

Project submission will be performed through Aula Global.
Two submission links will be enabled:

\begin{itemize}

\item \textgood{Report}. 
      It will contain the project report,
      which will be a file in PDF format named \textmark{report.pdf}.

\item \textgood{Source code}: 
      It will contain all the source code that is needed to compile.
\begin{itemize}
  \item It shall be a compressed file (ZIP format) named
        \textmark{fluid.zip}.
\end{itemize}

\end{itemize}

The project report shall not exceed 15 pages with a font size of 10 points
or higher, including title-page and all sections. If there are more than
15 pages, page 16 and above will not be considered during grading.
The report shall contain, at least, the following sections:

\begin{itemize}

\item \textmark{Title-page}: It shall contain the following information:
  \begin{itemize}
    \item Project name.
    \item Reduced group where students are enrolled.
    \item Team number.
    \item Name and NIA of all authors.
  \end{itemize}

\item \textmark{Original design}. 
      It shall include the design for each component in libraries.
      In this section and explanation and justification for the main
      design decisions must be included.

\item \textmark{Optimization}. 
      It shall contain a discussion of applied optimizations and their
      impact. In particular, it shall specify optimizations performed
      on the original source code, as well as optimizations enabled
      with additional compiler flags.

\item \textmark{Performed tests}: 
      Testing plan description to ensure correct execution.
      It shall include both unit tests and functional tests.

\item \textmark{Performance and energy evaluation}:
      It shall include performance and energy evaluations that have been
      carried out.

\item \textmark{Work organization}:
      It must describe the work organization among team members, 
      making explicit the tasks that each person in the team has performed.
      It must include the time dedicated by each person to each task.
      More than one person cannot be assigned to the same task.

\item \textmark{Conclusions}.
      Special value will be given to conclusions derived from performance evaluation
      results, as well as those conclusions relating the performed work with
      contents of the course.

\end{itemize}

