\subsubsection{Accelerations computation}

The following steps are performed

\begin{enumerate}
\item Initialize accelerations.
\item Densities increase.
\item Density transformation.
\item Acceleration transfer.
\end{enumerate}

\paragraph{Initialize densities and accelerations}.
During this step an initial value is given to the density ($\rho_i$) and the
vector acceleration ($\vec{a_i}$) for each particle.

The density is initially set to \cppid{0}.
\[
\rho_i = 0
\]

The vector acceleration is initially set to the \textgood{external acceleration}.

\[
\vec{a}_i = \vec{g}
\]

\paragraph{Densities increase}
In this step, for every block in the simulation grid all contiguous blocks as
well as the current block are considered. For every pair of particles $i$ and
$j$, the densities are increased.

\[
\Delta \rho_{ij} = 
    \begin{cases}
      (h^2 - \|\vec{p_i} - \vec{p_j}\|^2)^3 & 
          \text{if  } \|\vec{p_i} - \vec{p_j}\|^2 < h^2\\
      0 & 
          \text{if  } \|\vec{p_i} - \vec{p_j}\|^2 \geq h^2\\
    \end{cases}
\]

Note that density increase $\Delta \rho_{ij}$ is to be applied to both particles:
$i$ and $j$.

\[
\begin{split}
\rho_i = \rho_i + \Delta \rho_{ij}\\
\rho_j = \rho_j + \Delta \rho_{ij}\\
\end{split}
\]

However, special care needs to be taken to avoid that a particle is increased twice
with the same increment (as $\Delta \rho_{ij} = \Delta \rho_{ji}$).


\paragraph{Density transformation}
For every computed density, a linear transformation is performed.

\[
\rho_i = (\rho_i + h^6) \cdot \frac{315}{64 \cdot \pi \cdot h^9} \cdot m
\]

\paragraph{Acceleration transfer}
In this step, for every block in the simulation grid all contiguous blocks as
well as the current block are considered. For every pair of particles $i$ and
$j$, distances are evaluated.

If the two particles are near enough
($\|\vec{p_i} - \vec{p_j}\|^2 < h^2$) 
acceleration is updated.

\[
\begin{split}
& dist_{ij} = \sqrt{\max(\|\vec{p_i} - \vec{p_j}\|^2, 10^{-12})} \\
& \Delta \vec{a}_{ij} = 
  \frac{
    (\vec{p_i} - \vec{p_j}) \cdot \dfrac{15}{\pi \cdot h^6} \cdot
    \dfrac{3 \cdot m \cdot p_s}{2} \cdot 
    \dfrac{(h - dist_{ij})^2}{dist_{ij}} \cdot (\rho_i + \rho_j - 2 \cdot \rho) +
    (\vec{v_j} - \vec{v_i}) \cdot \dfrac{45}{\pi \cdot h^6} \cdot \mu \cdot m
  }{
    \rho_i \cdot \rho_j    
  } \\
& \vec{a}_i = \vec{a}_i + \Delta \vec{a}_{ij}\\
& \vec{a}_j = \vec{a}_j - \Delta \vec{a}_{ij}\\
\end{split}
\]

However, special care needs to be taken to avoid that a particle is increased twice
with the same increment (as $\vec{a}_{ij} = \vec{a}_{ji}$).
